A free/open-source Kazakh-Tatar machine translation system

### 2013-04-22 paper/paper.tex
abstract

\begin{document}
\spacing{1}
\maketitle
\begin{abstract}
This paper presents a bidirectional machine translation system between Kazakh and Tatar.
\todo{expand abstract}
\end{abstract}
%FIXME
%\maketitleabstract

>>>>

\begin{document}
\spacing{1}
\maketitle
\begin{abstract}
This paper presents a bidirectional machine translation system between Kazakh and Tatar, two Turkic languages.  Background on the differences between the languages is presented, followed by how the system was designed to handle some of these differences.  We provide an evaluation of the system's performance and directions for future work.
\todo{expand abstract}
\end{abstract}
%FIXME
%\maketitleabstract
